BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-31 main.tex
Cleanup citations

\begin{table}[ht]
% \scalebox{0.8}{ % TODO: Not sure about scalebox yet.
    \begin{minipage}{.51\linewidth}
	   \centering
	   \caption{Benchmark results of the parallel branches models}
	   \label{tab:parallel-branches-benchmark}
	   \SetTblrInner{colsep=2pt}
	   \begin{tblr}{
	   		column{1-X} = {c},
	   		column{Y-Z} = {r},
	   		hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
	   		hline{8, 9} = {-}{dashed},
	   		vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
	   	}
	       \textbf{Branches} & \textbf{Branch Length} &\textbf{Runtime} & \textbf{States} \\
	       5 & 1 & 1 ms& 35 \\
	       10 & 1 & 3 ms& 1.027 \\
	       15 & 1 & 161 ms& 32.771 \\
	       16 & 1 & 360 ms& 65.539 \\
	       17 & 1 & 790 ms& 131.075 \\
	       20 & 1 & 8.803 ms& 1.048.579 \\
	       5 & 5 & 14 ms& 7.779 \\
	       3 & 20 & 11 ms& 9.264 \\
	   \end{tblr}
    \end{minipage}%
    \qquad
    \begin{minipage}{.5\linewidth}
	   \centering
	   \caption{Benchmark results of the realistic BPMN models}
	   \label{tab:realistic-models-benchmark}
	   \SetTblrInner{colsep=2pt}
	   \begin{tblr}{
	   		column{Y-Z} = {r},
	   		hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
	   		hline{5} = {-}{dashed},
	   		vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
	   	}
	   	   \textbf{Model name} &\textbf{Runtime} & \textbf{States} \\
	   	   e001~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
	   	   e002~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
	   	   e020~\cite{houhouFirstOrderLogicVerification2022} & 10 ms & 5356 \\
	   	   credit-scoring-async\footref{footnote:camundaResearch} & 1 ms & 60 \\
	   	   credit-scoring-sync\footref{footnote:camundaResearch} & 1 ms & 140 \\
	   	   dispatch-of-goods\footref{footnote:camundaResearch} & 1 ms & 103\\
	   	   recourse\footref{footnote:camundaResearch} & 1 ms & 77 \\
	   	   self-service-restaurant\footref{footnote:camundaResearch} & 1 ms & 190 \\
	   \end{tblr}
    \end{minipage} 
% }
\end{table}

@@

\textbf{Tool capabilities:}
Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
Some tools investigate additional aspects, such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022,camundaservicesgmbhBpmnjsTokenSimulation2024}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.

>>>>

\begin{table}[ht]
% \scalebox{0.8}{ % TODO: Not sure about scalebox yet.
    \begin{minipage}{.51\linewidth}
	   \centering
	   \caption{Benchmark results of the parallel branches models}
	   \label{tab:parallel-branches-benchmark}
	   \SetTblrInner{colsep=2pt}
	   \begin{tblr}{
	   		column{1-X} = {c},
	   		column{Y-Z} = {r},
	   		hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
	   		hline{8, 9} = {-}{dashed},
	   		vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
	   	}
	       \textbf{Branches} & \textbf{Branch Length} &\textbf{Runtime} & \textbf{States} \\
	       5 & 1 & 1 ms& 35 \\
	       10 & 1 & 3 ms& 1.027 \\
	       15 & 1 & 161 ms& 32.771 \\
	       16 & 1 & 360 ms& 65.539 \\
	       17 & 1 & 790 ms& 131.075 \\
	       20 & 1 & 8.803 ms& 1.048.579 \\
	       5 & 5 & 14 ms& 7.779 \\
	       3 & 20 & 11 ms& 9.264 \\
	   \end{tblr}
    \end{minipage}%
    \begin{minipage}{.5\linewidth}
	   \centering
	   \caption{Benchmark results of the realistic BPMN models}
	   \label{tab:realistic-models-benchmark}
	   \SetTblrInner{colsep=2pt}
	   \begin{tblr}{
	   		column{Y-Z} = {r},
	   		hline{1, 2, Z} = {-}{1.2pt, solid}, % Z is the last row/column
	   		hline{5} = {-}{dashed},
	   		vline{2-Y} = {2-Z}{solid}, % Y is the second to last row/column
	   	}
	   	   \textbf{Model name} &\textbf{Runtime} & \textbf{States} \\
	   	   e001~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
	   	   e002~\cite{houhouFirstOrderLogicVerification2022} & 1 ms & 39 \\
	   	   e020~\cite{houhouFirstOrderLogicVerification2022} & 10 ms & 5356 \\
	   	   credit-scoring-async\footref{footnote:camundaResearch} & 1 ms & 60 \\
	   	   credit-scoring-sync\footref{footnote:camundaResearch} & 1 ms & 140 \\
	   	   dispatch-of-goods\footref{footnote:camundaResearch} & 1 ms & 103\\
	   	   recourse\footref{footnote:camundaResearch} & 1 ms & 77 \\
	   	   self-service-restaurant\footref{footnote:camundaResearch} & 1 ms & 190 \\
	   \end{tblr}
    \end{minipage} 
% }
\end{table}

@@

\textbf{Tool capabilities:}
Another way to compare the different BPMN formalizations and analysis tools is to investigate their capabilities.
Most tools formalize large parts of the BPMN specification and allow soundness and safeness checking~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021,houhouFirstOrderLogicVerification2022}.
Some tools investigate additional aspects, such as the introduction of \textit{data} and \textit{time} during verification~\cite{houhouFirstOrderLogicVerification2022,corradiniFormalisingAnimatingMultiple2022}.
Furthermore, other tools allow specifying and checking \textit{custom temporal logic properties}~\cite{krauterHigherorderTransformationApproach2024,corradiniFormalApproachAnalysis2021} and even provide graphical interfaces to ease the specification~\cite{krauterHigherorderTransformationApproach2024}.
Moreover, some tools provide interactive BPMN simulation using token-flow animation~\cite{corradiniFormalisingAnimatingMultiple2022}, while others \textit{visualize counterexamples} for soundness violations using tokens~\cite{houhouFirstOrderLogicVerification2022}.
